\begin{acknowledgements}      
\normalsize{
With reverential pranams, we express our sincere gratitude and salutation
to His Holiness Dr. Sree Sivakumara Swamigalu of Sree siddaganga
Mutt for his unlimited blessings. First and foremost, we wish to express
our deep sincere feelings of gratitude to our institution, Siddaganga Institute
of Technology for providing us for completing our project successfully.
We are grateful to Dr. M.N. Channabasappa, Director, Siddaganga Institute
of Technology, Tumakuru for his cooperation and encouragement.
We express our kind thanks to Dr. Shivananda K P, principal, Siddaganga
Institute of Technology Tumakuru for his encouragement towards
student’s attitude.\\
We express our heartfelt thanks to Dr. R. Sumathi, Professor and Head,
Department of Computer Science and Engineering, Siddaganga Institute
of Technology, Tumakuru for her suggestions and advice. We express
our gratitude and humble thanks to our project guide Mr. H.K Vedamurhty,
Assistant Professor, Department of Computer Science and Engineering,
Siddaganga Institute of Technology, Tumakuru for guiding and facilitating
to complete our Major-Project successfully.\\
We are conscious of the fact that we have received cooperation in many
ways from the Teaching, Technical and supporting staffs of the Department
of Computer Science and Engineering and we are grateful to all for
their cooperation.\\
We express heartfelt gratitude to our parent and friends for their constant
moral support and encouragement throughout this work.
}
\vspace{1.5cm}

\end{acknowledgements}

% ------------------------------------------------------------------------

